Jager: Symbolic Specification-Based Program Adjustment

### 2013-04-29 paper/paper.tex
Removing the windows carriage return character from the ends of paragraphs and formatting the paragraphs so that they fall into 80 character or less lines.

\subsection{Future Work}
Reduce size of queries via...
Removing redundant top traces
Looking for merge points between traces to reduce number of variables used in whole query
Remove impossible bottom traces based on top traces
Basically if variable unassociated with bug is constraint in top and bottom in infeasible way, then throw it out.
Look into removing variables that aren't involved in bug from consideration
Perhaps through postcondition raising

Integrate steps 1, 2 into single step
Increase complexity of grammars
Investigate dependent bugs by pairing statements

>>>>

\subsection{Future Work}

Reduce size of queries via...

Removing redundant top traces

Looking for merge points between traces to reduce number of variables used in whole query

Remove impossible bottom traces based on top traces

Basically if variable unassociated with bug is constraint in top and bottom
in infeasible way, then throw it out.

Look into removing variables that aren't involved in bug from consideration

Perhaps through postcondition raising

Integrate steps 1, 2 into single step

Increase complexity of grammars

Investigate dependent bugs by pairing statements
